---
title: "regression_analysis"
output: html_document
date: "2025-01-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
data <- read.csv('hpv_engagement_en&fr.csv')
```

```{r}
summary(data)
```
```{r}
summary(data$engagement)
hist(data$engagement)
```
```{r}
ggplot(data, aes(language, engagement)) +
  geom_boxplot(colour = c("coral1", "turquoise3")) +
  scale_x_discrete(labels = c("English", "French")) +
  labs(x = "Language", y = "Engagement per tweet",
       title = "The distribution of each tweet’s engagement by language") +
  theme_minimal() +
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5),
        aspect.ratio = 1/1) +
  annotate("text", x = 1, y = 38, size = 3.3, label = "Mean = 9.9") +
  annotate("text", x = 1, y = 229, size = 3.3, label = "Max = 192") +
  annotate("text", x = 2, y = 45, size = 3.3, label = "Mean = 43") +
  annotate("text", x = 2, y = 1633, size = 3.3, label = "Max = 1592")
```

```{r}
data_plot <- data %>%
  group_by(language) %>%
  summarize(engagement_mean = mean(engagement))

ggplot(data_plot, aes(x = language, y = engagement_mean)) + 
  geom_col(aes(fill = language), width = 0.4) + 
  geom_text(aes(label = round(engagement_mean, 1)), vjust = -0.5) +
  labs(x = "Language", y = "Average engagement (count)", 
       title = "The difference in engagement between English and French") + 
  theme_minimal() + 
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5),
        aspect.ratio = 1/1) +
  scale_x_discrete(labels = c("English", "French"))
```
```{r}
ggplot(data, aes(x = as.factor(language), y = engagement)) +
  geom_violin(aes(fill = as.factor(language)), alpha = 0.8) +
  geom_point(data = data_plot, aes(x = as.factor(language), y = engagement_mean), 
             color = "black", size = 1.2) +
  geom_text(data = data_plot, aes(x = as.factor(language), y = engagement_mean, 
                                   label = round(engagement_mean, 1)), hjust = -0.4, vjust = 0.1, color = "black") +
  labs(x = "Language", y = "Engagement", title = "Engagement distribution by language") +
  scale_x_discrete(labels = c("English", "French")) +
  theme_minimal() +
  theme(legend.position = "none")
```
```{r}
data_en <- subset(data, language == "en")
```

```{r}
ggplot(data_en, aes(x = language, y = engagement)) +
  geom_violin(aes(fill = language), draw_quantiles = 0.5, alpha = 0.8) +
  labs(x = "English", y = "Engagement") +
  theme_minimal() +
  theme(legend.position = "none", aspect.ratio = 3/2) +
  annotate("text", x = 0.7, y = 10, size = 3.8, label = "Mean = 9.9") +
  annotate("text", x = 1, y = 198, size = 3.8, label = "Max = 192") +
  scale_x_discrete(labels = NULL)
```
```{r}
data_fr <- subset(data, language == "fr")
```

```{r}
ggplot(data_fr, aes(x = language, y = engagement)) +
  geom_violin(fill = "turquoise3", draw_quantiles = 0.5, alpha = 0.8) +
  labs(x = "French", y = "Engagement") +
  theme_minimal() +
  theme(legend.position = "none", aspect.ratio = 3/2) +
  annotate("text", x = 0.7, y = 45, size = 3.8, label = "Mean = 43") +
  annotate("text", x = 1, y = 1619, size = 3.8, label = "Max = 1592") +
  scale_x_discrete(labels = NULL)
```

```{r}
data$language <- as.factor(data$language)
model_nb <- glm.nb(engagement ~ language, data)
summary(model_nb)
```
Because of the over-dispersed data with many extreme values, the negative binomial regression is used to regress the natural logarithm of the y-variable (language) on the x-variable (engagement). English is the baseline category here. The intercept indicates that the mean engagement count for tweets in English is about e^2.2908 = 9.88. As the coefficient of languagefr shows, tweets in French have on average approximately e^1.4711 = 4.354 times higher engagement than English, i.e., the mean engagement count for tweets in French is about 43.02. The extremely small p-value indicates that this result is statistically significant.

```{r}
en <- read.csv("dataset_en_hpv.csv")
```

```{r}
vars <- c("X", "full_text", "likes_count", "quotes_count", "replies_count", "retweets_count", "user_is_verified", "engagement")
new_en <- en[vars]
```

```{r}
new_en$user_is_verified <- as.factor(new_en$user_is_verified)
new_en$verified <- as.numeric(new_en$user_is_verified)
```

```{r}
model_lm <- lm(engagement ~ likes_count + quotes_count + replies_count + retweets_count + verified, new_en)
summary(model_lm)
```

```{r}
cor(new_en[, c("likes_count", "quotes_count", "replies_count", "retweets_count", "verified", "engagement")])
```
```{r}
# Engagement components preparation
en_plot <- new_en %>%
  pivot_longer(cols = c(likes_count, quotes_count, replies_count, retweets_count),
               names_to = "variable",
               values_to = "value")
```

```{r}
# Stats preparation
reg_stats <- en_plot %>%
  group_by(variable) %>%
  summarise(model = list(lm(engagement ~ value, data = cur_data())), 
            # cur_data() ensures that the function inside summarise() operates on only the relevant sub-data 
            r_squared = summary(model[[1]])$r.squared,
            # Double [] to extract the actual element from the list (model is a list here)
            correlation = sqrt(r_squared) * sign(coef(model[[1]])[2]),
            # sign function shows the correct direction of the relationship, although here are all positive
            p_value = summary(model[[1]])$coefficients[2, 4])
            # Values below 0.001 will be shown as "<0.001"

# Labels preparations
reg_stats <- reg_stats %>%
  mutate(label = paste0("r = ", round(correlation, 2), "\n",
                        "R² = ", round(r_squared, 2), "\n",
                        "p ", format.pval(p_value, digits = 2, eps = 0.001)))
```

```{r}
ggplot(en_plot, aes(value, engagement)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", colour = "firebrick3", se = TRUE) +
  geom_text(data = reg_stats, aes(x = Inf, y = Inf, label = label), inherit.aes = FALSE,
            hjust = 1, vjust = 4, size = 2.5, colour = "black") +
  facet_wrap(~ variable, scales = "free_x", axes = "all_y") +
  labs(x = "Engagement component", y = "Engagement (count)", 
       title = "Regression of engagement on components for tweets in English") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
fr <- read.csv("dataset_fr_hpv.csv")
```

```{r}
new_fr <- fr[vars]

new_fr$user_is_verified <- as.factor(new_fr$user_is_verified)
new_fr$verified <- as.numeric(new_fr$user_is_verified)
```

```{r}
model_lm_fr <- lm(engagement ~ likes_count + quotes_count + replies_count + retweets_count + verified, new_fr)
summary(model_lm_fr)
```
```{r}
cor(new_fr[, c("likes_count", "quotes_count", "replies_count", "retweets_count", "verified", "engagement")])
```

```{r}
# Engagement components preparation
fr_plot <- new_fr %>%
  pivot_longer(cols = c(likes_count, quotes_count, replies_count, retweets_count),
               names_to = "variable",
               values_to = "value")
```

```{r}
# Stats preparation
reg_stats_fr <- fr_plot %>%
  group_by(variable) %>%
  summarise(model = list(lm(engagement ~ value, data = cur_data())), 
            # cur_data() ensures that the function inside summarise() operates on only the relevant sub-data 
            r_squared = summary(model[[1]])$r.squared,
            # Double [] to extract the actual element from the list (model is a list here)
            correlation = sqrt(r_squared) * sign(coef(model[[1]])[2]),
            # sign function shows the correct direction of the relationship, although here are all positive
            p_value = summary(model[[1]])$coefficients[2, 4])
            # Values below 0.001 will be shown as "<0.001"

# Labels preparations
reg_stats_fr <- reg_stats_fr %>%
  mutate(label = paste0("r = ", round(correlation, 2), "\n",
                        "R² = ", round(r_squared, 2), "\n",
                        "p ", format.pval(p_value, digits = 2, eps = 0.001)))
```

```{r}
ggplot(fr_plot, aes(value, engagement)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", colour = "royalblue", se = TRUE) +
  geom_text(data = reg_stats_fr, aes(x = Inf, y = Inf, label = label), inherit.aes = FALSE,
            hjust = 1, vjust = 4, size = 2.5, colour = "black") +
  facet_wrap(~ variable, scales = "free_x", axes = "all_y") +
  labs(x = "Engagement component", y = "Engagement (count)", 
       title = "Regression of engagement on components for tweets in French") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

